---
title: "糖尿病 預測模型"
output: github_document
---

```{r setup, include=FALSE}

```

## 資料前處理
### 解釋資料


This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

### 把資料讀進來

You can include R code in the document as follows:

```{r echo=TRUE}
install.packages("mlbench")#此package內有很多dataset可練習

library(mlbench)#讀資料 糖尿病資料集

data(PimaIndiansDiabetes)#雙號

str(PimaIndiansDiabetes)#diabetes:pos陽性/neg陰性

#資料前處理
PimaIndiansDiabetesC<-#雙號

PimaIndiansDiabetes[complete.cases(PimaIndiansDiabetes),]#選資料完整的row

c(nrow(PimaIndiansDiabetes),nrow(PimaIndiansDiabetesC))
```

## 分成訓練組跟測試組,並紀錄各組人數

隨機將2/3的資料分到訓練組（Test==F），剩下1/3為測試組（Test==T）

```{r pressure, echo=FALSE}
PimaIndiansDiabetes$Test<-F 
PimaIndiansDiabetes[sample(1:nrow(PimaIndiansDiabetes),nrow(PimaIndiansDiabetes)/3),]$Test<-T 
c(sum(PimaIndiansDiabetes$Test==F),sum(PimaIndiansDiabetes$Test==T)) 

```

可得訓練組案例數為'r sum(PimaIndiansDiabetes$Test==F)'，測試組案例數為'r sum(PimaIndiansDiabetes$Test==T)'
